Sequential algorithms to split and merge terabyte-scale 3D images

### 2017-06-11 paper.tex
Explained nseeks for cluster reads

As detailed in Algorithm~\ref{algo:cluster-reads}, cluster reads load
multiple blocks in memory, concatenate them in a buffer and write the
buffer as sequentially as possible. The buffer is a slightly complex
data structure, for instance an associative array or Python
dictionary, capable of storing multiple disjoint sequences of
contiguous bytes without having to allocate memory to store the
``holes'' between such sequences \todo{a figure showing the buffer and
  how it fillus up would help}.  \note{More on defragmentation might
  be needed here.}
\begin{algorithm}[h]
  \caption{Buffered merging from blocks using cluster reads}
  \label{algo:cluster-reads}
  \begin{algorithmic}
    \STATE list = sort blocks by increasing (x,y,z) values
    \STATE initialize buffer
    \STATE index = 0
    \WHILE{index\textless n}
      \WHILE{sizeof(buffer)\textless m}
        \STATE block = list[index]
        \STATE read block and insert it in buffer
        \STATE index += 1
        \ENDWHILE
       \STATE write buffer in reconstructed image
       \STATE clear buffer
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

\begin{equation}
  N_\mathrm{cluster\_reads}= n + \ceil*{\frac{bR}{m}}f(m,n,R)
\end{equation}
where:
\begin{equation}
  f(m,n,R)=
  \begin{cases}
    d^2 & $if there is an incomplete line$\\
    d   & $if there is an incomplete slice$\\
    1   & $otherwise$
\end{cases}
\end{equation}

>>>>

As detailed in Algorithm~\ref{algo:cluster-reads}, cluster reads load
multiple blocks in memory, concatenate them in a buffer and write the
buffer as sequentially as possible. The buffer is a slightly complex
data structure, for instance an associative array or a Python
dictionary, capable of storing multiple disjoint sequences of
contiguous bytes without having to allocate memory for the bytes
between such sequences. Implementation details about the buffer are
given later in the document.

\todo{a figure showing the buffer and how it
  fillus up would help}.
%\note{More on defragmentation might be
%  needed here.}
\begin{algorithm}[h]
  \caption{Buffered merging from blocks using cluster reads}
  \label{algo:cluster-reads}
  \begin{algorithmic}
    \STATE list = sort blocks by increasing (x,y,z) values
    \STATE initialize buffer
    \STATE index = 0
    \WHILE{index\textless n}
      \WHILE{sizeof(buffer)\textless m}
        \STATE block = list[index]
        \STATE read block and insert it in buffer
        \STATE index += 1
        \ENDWHILE
       \STATE write buffer in reconstructed image
       \STATE clear buffer
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

The number of seeks performed by cluster reads depends on the way that
blocks loaded in memory arrange in the reconstructed image. In the
best case, blocks in memory completely cover slices in the
reconstructed image. In this case, slices of the reconstructed images
can be written without seeking at all. If the blocks in memory
completely cover rows in the reconstructed image but do not cover
entire slices, then the blocks are written with $d$ seeks, one per
slice. And if the blocks do not cover entire rows, then they are
written with $d^2$ seeks, one per row and per slice.  In conclusion:
\begin{equation}
  N_\mathrm{cluster\_reads}= n + \ceil*{\frac{bR}{m}}f(m,n,R)
\end{equation}
where:
\begin{equation}
  f(m,n,R)=
  \begin{cases}
    d^2 & $if there is an incomplete row$\\
    d   & $if there is an incomplete slice but not incomplete row$\\
    1   & $otherwise$
\end{cases}
\end{equation}
